Figure 2c

### 2018-05-12 inst/lncTAM34a_KD/lncTAM34a_KD.Rmd
lncTAM34a KD analysis and figure

---
title: "Figure 3a"
subtitle: "miR34a asRNA stable over-expression cell lines"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

@@

data <- getData("Figure 2c")
#data <- read_tsv('~/Github/miR34a_asRNA_project/data-raw/lncTAM34a_KD.txt')

@@

p <- ggplot(data = NULL) +
  geom_dotplot(
    data = data, 
    aes(
      x = `GOI`,
      y = fold,
      fill = siRNA
    ),
    binwidth = 0.01,
    colour = NA,
    #alpha = 0.5,
    position = position_dodge(width = 0.9), 
    binaxis = 'y', 
    stackdir = 'center',
    dotsize = 1,
    show.legend = TRUE
  ) +
  scale_y_continuous("Fold")+
  labs(x = "Gene")

@@

pdf <- p +
  geom_linerange(
    data = stats,
    aes(
      x = GOI,
      ymin = CI95l.linear,
      ymax = CI95h.linear,
      group = interaction(siRNA, GOI)
    ),
    position = position_dodge(width = 0.9),
    colour = "grey30",
    size = 0.3,
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = GOI,
      y = mean.linear,
      group = interaction(siRNA, GOI)
    ),
    colour = "grey30",
    shape = 95,
    size = 4,
    position = position_dodge(width = 0.9),
    show.legend = FALSE
  ) +
  geom_label(
    data = vl,
    aes(
      x = label, 
      y = max + 0.075, 
      label = pFormat, 
      group = interaction(siRNA, GOI)
    ),
    fill = "white",
    colour = "grey30",
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fontface = "bold",
    family = "Arial Unicode MS",
    size = 2.5
  ) +
  geom_segment(
    data = vl,
    aes(
      x = x,
      y = max + 0.05,
      xend = xend,
      yend = max + 0.05
    ),
    colour = "grey30",
    size = 0.3,
    show.legend = FALSE
  ) +
  guides(
    fill = guide_legend(
      title = "Gene", 
      override.aes = list(size = 4)
    )
  )

@@

path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 2c"][[1]])
ggsave(
  plot = figure,
  filename = path,
  device = cairo_pdf,
  height = 60,
  width = 83,
  units = "mm"
)
```

>>>>

---
title: "Figure 2c"
subtitle: "miR34a asRNA knock down in U2Os cells"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

@@

data <- getData("Figure 2c")

@@

p <- ggplot(data = NULL) +
  geom_dotplot(
    data = data, 
    aes(
      x = `GOI`,
      y = fold,
      fill = siRNA
    ),
    binwidth = 0.01,
    colour = NA,
    #alpha = 0.5,
    position = position_dodge(width = 0.9), 
    binaxis = 'y', 
    stackdir = 'center',
    dotsize = 4,
    show.legend = TRUE
  ) +
  scale_y_continuous("Fold")+
  labs(x = "Gene")

@@

pdf <- p +
  geom_linerange(
    data = stats,
    aes(
      x = GOI,
      ymin = CI95l.linear,
      ymax = CI95h.linear,
      group = interaction(siRNA, GOI)
    ),
    position = position_dodge(width = 0.9),
    colour = "grey30",
    size = 0.3,
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = GOI,
      y = mean.linear,
      group = interaction(siRNA, GOI)
    ),
    colour = "grey30",
    shape = 95,
    size = 4,
    position = position_dodge(width = 0.9),
    show.legend = FALSE
  ) +
  geom_label(
    data = vl,
    aes(
      x = label, 
      y = max + 0.1, 
      label = pFormat, 
      group = interaction(siRNA, GOI)
    ),
    fill = "white",
    colour = "grey30",
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fontface = "bold",
    family = "Arial Unicode MS",
    size = 2.5
  ) +
  geom_segment(
    data = vl,
    aes(
      x = x,
      y = max + 0.05,
      xend = xend,
      yend = max + 0.05
    ),
    colour = "grey30",
    size = 0.3,
    show.legend = FALSE
  ) +
  guides(
    fill = guide_legend(
      title = "Gene", 
      override.aes = list(size = 4)
    )
  )

@@

path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 2c"][[1]])
ggsave(
  plot = figure,
  filename = path,
  device = cairo_pdf,
  height = 60,
  width = 68,
  units = "mm"
)
```
